Exploring the structure of the bound proton with Deeply Virtual Compton Scattering

### 2019-03-08 eg6-letters/incoherent/incoherent_prl.tex
latest comments from Stepan

\date{\today}
\begin{abstract}
In the past two decades, deeply virtual Compton scattering of electrons has been successfully 
used to advance our knowledge of the partonic structure of the free proton and investigate 
correlations between the transverse position and the longitudinal momentum of quarks inside 
the nucleon.  The structure of bound nucleons in nuclei has only been studied in inclusive
deep-inelastic lepton scattering experiments off nuclear targets, showing a significant
difference in longitudinal momentum distribution of quarks inside the bound nucleon, known as
the EMC effect.  In this work, we report the first beam spin asymmetry (BSA) measurement of
exclusive deeply virtual Compton scattering (DVCS) off a proton bound in $^4$He.  The data
used here were accumulated using a $6$ GeV longitudinally polarized electron beam incident on
a pressurized $^4$He gaseous target placed within the CLAS spectrometer in Hall-B at the Thomas
Jefferson National Accelerator Facility. The azimuthal angle ($\phi$) dependence of the BSA was
studied in a wide range of virtual photon and scattered proton kinematics. The Q$^2$, x$_B$,
and t dependencies of the BSA on the bound proton are compared with those on the free proton.
In the whole kinematical region of our measurements, the BSA on the bound proton is smaller by
20\% to 40\%, indicating possible medium modification of its partonic structure.
\end{abstract}
%\pacs{Valid PACS appear here}

@@

Following the cross section decomposition provided in \cite{Belitsky:2001ns}, 
the different components can be expressed in terms of Fourier coefficients 
associated with $\phi$-harmonics, where $\phi$ is the angle between the 
leptonic and the hadronic planes of the reaction. At leading-twist, the BSA can 
be parameterized as: 
\begin{equation}
   A_{LU}(\phi) = \frac{a_{0}\sin(\phi)}{1+a_{1}\cos(\phi)+a_{2}\cos(2\phi)},
   \label{eq:alu-simp}
\end{equation}
where the parameters $a_{0,1,2}$ are combinations of the aforementioned Fourier 
coefficients. The $\sin(\phi)$ harmonic is dominant in $A_{LU}$ and is 
proportional to the following combination of Compton form factors (CFF) 
$\mathcal{H}$, $\mathcal{E}$, and $\tilde{\mathcal{H}}$ as  
\cite{Guidal:2013rya}
\begin{equation}
   a_{0} \propto \operatorname{Im}( F_1 \mathcal{H}- \frac{t}{4M^2} F_2 
   \mathcal{E}+ \frac{x_B}{2}(F_1+F_2)\tilde{\mathcal{H}}),
\end{equation}
where $F_1$ and $F_2$ are the Dirac and Pauli form factors, respectively, and 
$x_B$ the Bjorken scaling variable. The real and the imaginary parts of the CFF 
$\mathcal{H}$ relate to the GPD $H$ as  \begin{align}
   \Re(&\mathcal{H}) = \mathcal{P} \int_{0}^{1}dx[H(x,\xi,t)-H(-x,\xi,t)] \, 
   C^{+}(x,\xi), \\
   \Im(&\mathcal{H}) = - \pi [H(\xi,\xi,t)-H(-\xi,\xi,t)],
\end{align}
with $\mathcal{P}$ the Cauchy principal value integral and $C^{+}$ a 
coefficient function defined as $(1/(x-\xi) + 1/(x+\xi))$, where $\xi$ is the 
skewing factor and can be related to $x_B$ by $\xi\approx {{x_B}\over{2-x_B}}$.  
Similar expressions apply for the GPDs $E$, $\widetilde{H}$, and 
$\widetilde{E}$ \cite{Guidal:2013rya}.

@@

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. 
First, events were selected with $Q^2$ grater than $1$ GeV$^2$ and the 
$\gamma^*p$ invariant mass ($W=\sqrt{(q+p)^2}$, assuming that the initial 
nucleon is at rest) greater than $2$ GeV. This is a commonly accepted region of 
kinematics used by the previous DVCS experiments to ensure the applicability of 
the DVCS handbag diagram and avoid the nucleon resonance region. The squared 
transferred momentum to the recoil proton $t$, calculated from the 
four-momentum vectors of the incoming and outgoing photons, was required to be 
greater than a minimum kinematically allowed value ($t_{min}$) at given $Q^2$ 
and $W$ defined as: \begin{equation}
t_{min} 
   =-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}},
\end{equation}
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass. This cut was applied to avoid accepting events in unphysical 
regions of kinematics for which it is not possible to calculate the radiative 
effects. We specifically use the 
kinematics of the photons to determine $t$ because the initial proton 
kinematics is unknown due to Fermi motion.

@@

In the kinematical phase-space of our experiment, the GPD $H$ is
expected to dominate the contribution in the BSA over the other three GPDs.  
There, the $\phi$ dependence of $A_{LU}$ is mostly sensitive to the  imaginary 
part of the CFF $\mathcal{H}$ through the parameter $a_0$ of 
equation~\ref{eq:alu-simp}. The measurement of the free proton $A_{LU}$ 
\cite{Girod:2007aa} has confirmed that the $a_0$ term dominates the shape of 
the distribution.

@@

%conclusion
In summary, we have presented the first BSA measurement associated with bound 
proton DVCS off $^4$He using an upgraded setup of the CLAS spectrometer at 
Jefferson Lab. Our results are compared to model calculations based on 
different assumptions of the nuclear medium effects at the partonic level. The 
bound-proton BSA is largely suppressed compared to the free proton BSA. This 
result is a first step in using a novel experimental method of understanding 
the properties of bound nucleons directly from the basic degrees of freedom of 
QCD, quarks and gluons. Planned experiments at Jefferson Lab will continue 
and extend these studies of the bound nucleon structure using DVCS. We have 
an experimental program using the CLAS12 detector in the experimental Hall-B, 
called ALERT, to improve the DVCS measurements with the detection of nuclear
fragments to better control the final state interactions and the initial state
kinematic of the bound nucleon.

>>>>

\date{\today}
\begin{abstract}
In the past two decades, deeply virtual Compton scattering of electrons has 
   been successfully used to advance our knowledge of the partonic structure of 
   the free proton and investigate correlations between the transverse position 
   and the longitudinal momentum of quarks inside the nucleon. Meanwhile, the 
   structure of bound nucleons in nuclei has only been studied in inclusive 
   deep-inelastic lepton scattering experiments off nuclear targets, showing a 
   significant difference in longitudinal momentum distribution of quarks 
   inside the bound nucleon, known as
the EMC effect. In this work, we report the first beam spin asymmetry (BSA) 
   measurement of exclusive deeply virtual Compton scattering (DVCS) off a 
   proton bound in $^4$He.  The data used here were accumulated using a $6$ GeV 
   longitudinally polarized electron beam incident on
a pressurized $^4$He gaseous target placed within the CLAS spectrometer in Hall-B at the Thomas
Jefferson National Accelerator Facility. The azimuthal angle ($\phi$) dependence of the BSA was
studied in a wide range of virtual photon and scattered proton kinematics. The 
   $Q^2$, $x_B$,
and t dependencies of the BSA on the bound proton are compared with those on the free proton.
In the whole kinematical region of our measurements, the BSA on the bound proton is smaller by
20\% to 40\%, indicating possible medium modification of its partonic structure.
\end{abstract}
%\pacs{Valid PACS appear here}

@@

Following the cross section decomposition provided in \cite{Belitsky:2001ns}, 
the different components can be expressed in terms of Fourier coefficients 
associated with $\phi$-harmonics, where $\phi$ is the angle between the 
leptonic and the hadronic planes of the reaction. At leading-twist, the BSA can 
be parameterized as: 
\begin{equation}
   A_{LU}(\phi) = \frac{a_{0}\sin(\phi)}{1+a_{1}\cos(\phi)+a_{2}\cos(2\phi)},
   \label{eq:alu-simp}
\end{equation}
where the parameters $a_{0,1,2}$ are combinations of the aforementioned Fourier 
coefficients. The $\sin(\phi)$ harmonic is dominant in $A_{LU}$ and is 
proportional to the following combination of Compton form factors (CFF) 
$\mathcal{H}$, $\mathcal{E}$, and $\tilde{\mathcal{H}}$ as  
\cite{Guidal:2013rya}
\begin{equation}
   a_{0} \propto \operatorname{Im}( F_1 \mathcal{H}- \frac{t}{4M^2} F_2 
   \mathcal{E}+ \frac{x_B}{2}(F_1+F_2)\tilde{\mathcal{H}}),
   \label{a0_cff}
\end{equation}
where $F_1$ and $F_2$ are the Dirac and Pauli form factors, respectively, and 
$x_B$ the Bjorken scaling variable. The real and the imaginary parts of the CFF 
$\mathcal{H}$ relate to the GPD $H$ as  \begin{align}
   \Re(&\mathcal{H}) = \mathcal{P} \int_{0}^{1}dx[H(x,\xi,t)-H(-x,\xi,t)] \, 
   C^{+}(x,\xi), \\
   \Im(&\mathcal{H}) = - \pi [H(\xi,\xi,t)-H(-\xi,\xi,t)],
\end{align}
with $\mathcal{P}$ the Cauchy principal value integral and $C^{+}$ a 
coefficient function defined as $(1/(x-\xi) + 1/(x+\xi))$, where $\xi$ is the 
skewing factor and can be related to $x_B$ by $\xi\approx {{x_B}\over{2-x_B}}$.  
Similar expressions apply for the GPDs $E$, $\widetilde{H}$, and 
$\widetilde{E}$ \cite{Guidal:2013rya}. At forward limit, $\xi\to 0$ and $t \to 0$, the GPD H reduces to quark anti-quark PDFs and its 0th moment in $x$ represents the elastic Dirac form-factor F$_1$.

@@

Further requirements were applied to clean the identified initial set of 
incoherent DVCS events from accidental and physics background events. 
First, events were selected with $Q^2$ grater than $1$ GeV$^2$ and the 
$\gamma^*p$ invariant mass ($W=\sqrt{(q+p)^2}$, assuming that the initial 
nucleon is at rest) greater than $2$ GeV. This is a commonly accepted region of 
kinematics used by the previous DVCS experiments to ensure the applicability of 
the DVCS handbag diagram and avoid the nucleon resonance region. The squared 
transferred momentum to the recoil proton $t$, calculated from the 
four-momentum vectors of the incoming and outgoing photons, was required to be 
greater than a minimum kinematically allowed value ($t_{min}$) at given $Q^2$ 
and $W$ defined as: \begin{equation}
t_{min} 
   =-Q^{2}~\frac{2(1-~x_{B})(1~-~\sqrt{1~+~\epsilon^{2}})~+~\epsilon~^{2}}{4x_{B}(1-x_{B})+\epsilon^{2}},
\end{equation}
where $\epsilon^{2}=~\frac{4M^{2}_{p}x^{2}_{B}}{Q^{2}}$ and $M_{p}$ is the 
proton mass. This cut was applied to avoid accepting events that appear in  
unphysical regions of kinematics due to detector resolution and radiative 
effects.  We specifically use the kinematics of the photons to determine $t$ 
because the initial proton kinematics is unknown due to Fermi motion.

@@

In the kinematical phase-space of our experiment, the $\phi$ dependence of 
$A_{LU}$ is most sensitive to the imaginary part of the CFFs through the $a_0$ 
term of Eq.~\ref{eq:alu-simp}, as confirmed by high statistics measurements on 
the free proton \cite{Girod:2007aa,Jo:2015ema}. In the determination of $a_0$ 
in Eq.~\ref{a0_cff}, the CFF $\mathcal{E}$ and $\mathcal{\tilde {H}}$ are 
suppressed due to form-factors and the smallness of the coefficients.  
Therefore, the dominant contribution to the BSA comes from the CFF 
$\mathcal{H}$ and hence the GPD $H$.

@@

%conclusion
In summary, we have presented the first BSA measurement associated with bound 
proton DVCS off $^4$He using an upgraded setup of the CLAS spectrometer at 
Jefferson Lab. Our results are compared to model calculations based on 
different assumptions of the nuclear medium effects at the partonic level. The 
bound-proton BSA is largely suppressed compared to the free proton BSA. This 
result is a first step in using a novel experimental method of understanding 
the properties of bound nucleons directly from the basic degrees of freedom of 
QCD, quarks and gluons. Planned experiments at Jefferson Lab will continue 
and extend these studies of the bound nucleon structure using DVCS. We have an 
experimental program called ALERT using the CLAS12 detector in the Hall-B of 
Jefferson Lab. These experiments will improve the DVCS measurements with the 
detection of nuclear fragments to better control the final state interactions 
and the initial state kinematics of the bound nucleon.
